---
title: "Challenge #2"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Choosing low-quality associations
Here I will show how to create a filtered subset of data.  
Below, you will see the R script used to generate a new table from associations.tsv.  

```{r data}
associations <- read.csv("trpv1.tsv", sep="\t")
colnames(associations)[colnames(associations) == "X0.999"] <- "comb_score"
low_quality <- subset(associations, comb_score < 0.5)
new_file <- low_quality[,c(1,2,15)]
# Now let's see the filtered subset of our data
View(new_file)

```

**The original challenge was**

  Create an R script that ….  
 * Extracts all the low quality associations (combined score (last column) less than 0.5).  
 * Writes/saves the first two columns (node1 and node2 columns) and the combined scores column (last column), as a separate file.  
 * Modify this script as an R markdown file.  
 * Generate a HTML of this R markdown contents.  
 
 Let's see the filtered subset of our data...  
```{r associations, echo=FALSE}
print(new_file)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
